% LaTeX

\documentclass[12pt]{amsart} \usepackage{amssymb}

%\textwidth = 460pt 
%\textheight = 9in 
%\hoffset=-54pt \voffset=-40pt

% SIDE MARGINS:
\oddsidemargin 0in \evensidemargin 0in

% VERTICAL SPACING:
%\topmargin -.15in
\topmargin -.4in
\headheight 0in \headsep 0.0in
%\footheight 0.5in
\footskip 0.5in

\pagestyle{plain}
%\pagenumbering{}

% DIMENSION OF TEXT:
\textheight 10in \textwidth 6.5in
%

%\textwidth = 470pt
%\textheight = 700pt
%%\topmargin = 0pt
%%\oddsidemargin = 0pt
%\hoffset = -60pt
%\voffset = -50pt

%\input epsf \def\epsfsize#1#2{0.4#1\relax} \def\nl{\hfil\break}

%\renewcommand{\baselinestretch}{1.2}
%\def\Indent{\hskip .2in}


\title[]{Diversity Statement}

\begin{document}
\maketitle
\thispagestyle{empty}

In my mind,
diversity is an essential characteristic of a strong and stable environment and society.
In human history, it is precisely the existence of human genetic diversity that makes us able to resist many deadly diseases.
For example, Hemophilia is caused by defects in certain human genes.
It is fatal for human in the sense that the disease will cause human to keep bleeding.
However, in the Middle Ages when the Black Death prevailed,
these ``defected" genes saved many people from the Black Death because these genes can improve human's ability to combine iron ions,
which will help human more effectively fight diseases.
In our society and community, we should also respect diversity, the cultures of minorities and their potentials.

\section{Past experience to improve diversity}
When I was a senior student in my undergraduate,
I volunteered to participate a special tutoring program, where I was able to help middle school students from family with single parent.
I was very happy and honored to help the girl and to improve her mathematics and physics.
We still keep in touch and she's now studying in a good university in China.
I am proud of the experience that I could help those with misfortune in their family.

In my Ph.D period,
I was involved in the Intel International Science and Engineering Fair (Intel ISEF)  in Pittsburgh in May 2015,
which is world's largest international pre-college science competition.
The premier global science competition for students provides a forum for more than 1,700 students from 70 countries, 
regions, and territories to display their independent research. 
I served as a judger (totally 5 judgers) and sought for the best work on statistics side.
We identified five pieces of works in the first round of selection.
We finally gave the first prize to a primary school boy by his impressive presentation and solid statistical content.
Though other high school and middle school students are superior to primary school boy,
we felt the primary school boy did a fantastic job at his age and we should encourage diversity and attract more participation of younger groups.
I am proud of the experience that I can select the primary school boy as the best competition work.


\section{My own contribution of diversity}
I am senior Ph.D student in Biostatistics department at this stage.
Prior to that, I obtained a Master's degree in Physics in 2012 in University of Pittsburgh 
and a Bachelor's degree in Physics in 2011 in Harbin Institute of Technology in China.
I believe my experience in Physics will help expand the academic diversity in the field of statistics.
I am originally from northeastern part of China, which is comparatively undeveloped region.
Majority of oversea students of China are from southern parts of China or major big cities.
I will improve the representation of undeveloped region where limited education resources are allocated.

\end{document}
