%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{color,hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\fancyhf{}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}


\name{Zhiguang (Caleb) Huo} % Your name
\address{(412)-979-0592 \\ \url{zhh18@pitt.edu}} % Your phone number and email
\address{\url{http://www.pitt.edu/~zhh18/dev/}} % Your phone number and email
\address{4600 Bayard ST, APT 308, Pittsburgh, PA 15213} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

%------------------------------------------------
\begin{rSection}{Publications}
\textbf{Methodology} 
\begin{enumerate}[noitemsep,topsep=0pt]
\item  {\bf Zhiguang Huo}, Ying Ding, Silvia Liu, Steffi Oesterreich, and George Tseng. Meta-Analytic Framework for Sparse $K$-Means to Identify Disease Subtypes in Multiple Transcriptomic Studies. \emph{Journal of the American Statistical Association},  111, no. 513 (2016): 27-42.
    \item {\bf Zhiguang Huo}, Chi Song, George C. Tseng. (2016)
Bayesian latent hierarchical model for transcriptomic meta-analysis to detect biomarkers with clustered meta-patterns of differential expression signals. Submitted to \emph{Annals of Applied Statistics} (under second round of review).
    \item {\bf Zhiguang Huo}, George C. Tseng. (2016)
    Integrative Sparse $K$-means with overlapping group lasso in genomic applications for disease subtype discovery.
Submitted to \emph{Annals of Applied Statistics} (under second round of review).
\item Zhu, Li, Ying Ding, Cho-Yi Chen, Lin Wang, {\bf Zhiguang Huo}, SungHwan Kim, Christos Sotiriou, Steffi Oesterreich, and George C. Tseng. "MetaDCN: meta-analysis framework for differential co-expression network detection with an application in breast cancer." \emph{Bioinformatics} (2016): btw788.
\item SungHwan Kim, Dongwan Kang, {\bf Zhiguang Huo}, Yongseok
Park, George C. Tseng. (2016)
Meta-analytic principal component analysis in integrative omics application.
(Submitted).
    \item Silvia Liu, Wei-Hsiang Tsai, Ying Ding, Rui Chen, Zhou Fang, {\bf Zhiguang Huo}, SungHwan Kim, Tianzhou Ma, Ting-Yu Chang, Nolan Michael Priedigkeit, Adrian V. Lee, Jianhua Luo, Hsei-Wei Wang, I-Fang Chung, George C. Tseng. (2015).
Comprehensive evaluation of fusion transcript detection algorithms and a meta-caller to combine top performing methods in paired-end RNA-seq data.
\emph{Nucleic Acids Research}, 10.1093/nar/gkv1234.
    \item Xingbin Wang, Dongwan Kang, Kui Shen, Chi Song, Shuya Lu, Lunching Chang, Serena G. Liao, {\bf Zhiguang Huo}, Naftali Kaminski, Etienne Sibille, Yan Lin, Jia Li and George C. Tseng. (2012) A Suite of R Packages for Quality Control, Differentially Expressed Gene and Enriched Pathway Detection in Microarray Meta-analysis. \emph{Bioinformatics}, 28:2534-2536.
\end{enumerate}

\textbf{Application}
\begin{enumerate}[noitemsep,topsep=0pt,resume]
    \item  Dominique Arion, {\bf Zhiguang Huo}, John F. Enwright, John P. Corradi, George Tseng and David A. Lewis. (2016)
Transcriptome alterations in prefrontal pyramidal neurons distinguish schizophrenia from bipolar and major depressive disorders.
Submitted to \emph{Biological Psychiatry}, (under second round of review).

    \item Tiffany A. Katz, Serena G. Liao, Vincent J. Palmieri, Robert K. Dearth, Thushangi Pathiraja, {\bf Zhiguang Huo}, Patricia Shaw, Sarah Small, Nancy E. Davidson, David G. Peters, George C. Tseng, Steffi Oesterreich, Adrian V. Lee. (2015) Targeted DNA Methylation Screen in the Mouse Mammary Genome Reveals a Parity-Induced Hypermethylation of IGF1R That Persists Long after Parturition. \emph{Cancer Prevention Research} 8, no. 10 (2015): 1000-1009.

    \item Yan P. Yu, Silvia Liu, {\bf Zhiguang Huo}, Amantha Martin, Joel B. Nelson, George C. Tseng and Jian-Hua Luo. (2015) Genomic copy number variations in the genomes of leukocytes predict prostate cancer clinical outcomes. \emph{PloS one}, 10(8):e0135982.

\end{enumerate}

\textbf{Manuscript in Preparation}
\begin{itemize}
\item \textbf{Methodology}
\end{itemize}

\begin{enumerate}[noitemsep,topsep=0pt,resume]
\item  {\bf Zhiguang Huo}, Shaowu Tang, YongSeok Park and George Tseng. (2017)
Biomarker categorization and fast computing of adaptively weighted Fisher's method for meta-analysis in omics applications.
\item Li Zhu, {\bf Zhiguang Huo}, Tianzhou Ma, George Tseng. (2017)
Bayesian indicator variable selection model with multi-layer overlapping groups.
\item Tianzhou Ma$^*$, {\bf Zhiguang Huo}$^*$, Anche Kuo$^*$, Xiangrui Zeng, Li Zhu, Ark Fang, Lin Wang, Chien-Wei Lin, Tanbin Rahman, Shuchang Liu, YongSeok Park, Sunghwan Kim, George Tseng.  (2017)
MetaOmics - a Comprehensive Software Suite with Interactive Visualization for Transcriptomic Meta-Analysis.
($*$: co-first author).
\end{enumerate}

\begin{itemize}
\item \textbf{Application}
\end{itemize}

\begin{enumerate}[noitemsep,topsep=0pt,resume]
\item Enwright, John, Dominique Arion, John Corradi, Aiqing He, {\bf Zhiguang Huo}, George Tseng, and David Lewis. (2017) Transcriptome Profiling of Layer 3 Parvalbumin Neurons from the Dorsolateral Prefrontal Cortex of Schizophrenia Subjects.
\item Logan, R.W., Ozburn, A.R., {\bf Huo, Z.}, Zhu, X., Fitzgerald, E., Arey, R.N., Jarpe, M., Tseng, G. and McClung, C.A. (2017)
Valproic acid targets HDAC2 to normalize mania-like behaviors in mice. In preparation.

\item Rachel Puralewski, {\bf Zhiguang Huo}, George Tseng, Ryan Logan, Marianne Seney. (2017) Sex differences in basolateral amygdala transcriptome associated with effects of chronic stress. In preparation.

\item {\bf Zhiguang Huo}, Rachel Puralewski, George Tseng, Ryan Logan, Marianne Seney. (2017) Circuit-wide transcriptional profiling reveals sex differences in coherence patterns across brain regions. In preparation.

\end{enumerate}




\textbf{Book}
\begin{enumerate}[noitemsep,topsep=0pt,resume]
\item  George C. Tseng, {\bf Zhiguang Huo} and Tianzhou Ma. (2017)
Foundations for High-Throughput Omics Data Analysis: Methods, Theories and Applications. \emph{Chapman \& Hall/CRC}. 
(Under preparation).
\end{enumerate}

\textbf{Book Chapter}
\begin{enumerate}[noitemsep,topsep=0pt,resume]
\item SungHwan Kim,  {\bf Zhiguang Huo}, YongSeok Park and George Tseng.  (2015) MetaOmics: transcriptomic meta-analysis methods for biomarker detection, pathway analysis and other exploratory purposes. Book chapter in Integrating omics data: statistical and computational methods. Edited by George C. Tseng, Debashis Ghosh, Xianghong Jasmine Zhou. \emph{Cambridge University Press}. Page 39-67.

\end{enumerate}
\end{rSection}

\end{document}
